Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-06-05 manuscript/manuscript.Rmd
Add marginal effect plot.

friedman_test_result <- friedman.test(as.matrix(data[, "dataset" := NULL]))
```

Significant differences exist between process configurations (Friedman test: $p < 10^{-5})$.

@@

# Convert to data matrix. First aggregate within each experiment because the
# Wilcoxon signed rank test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ learner + transformation_method + normalisation_method, value.var="value_rank",
  fun.aggregate = mean
)

data[, "dataset" := NULL]
configurations <- colnames(data)
```

Something about direct comparisons.

@@

>>>>

h_overall <- friedman.test(as.matrix(data[, "dataset" := NULL]))
```

Significant differences exist between process configurations (Friedman test: $p < 10^{-8})$.

@@

# Convert to data matrix. First aggregate within each experiment because the
# Wilcoxon signed rank test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ learner, value.var="value_rank",
  fun.aggregate = mean
)

h_learner <- stats::wilcox.test(
    x = data[["random_forest_ranger"]],
    y = data[["glm"]],
    paired = TRUE,
    alternative = "two.sided"
)
```

# Convert to data matrix. First aggregate within each experiment because the
# Wilcoxon signed rank test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ normalisation_method, value.var="value_rank",
  fun.aggregate = mean
)

h_normalisation <- stats::wilcox.test(
    x = data[["none"]],
    y = data[["robust_standardisation"]],
    paired = TRUE,
    alternative = "two.sided"
)
```

# Convert to data matrix. First aggregate within each experiment because the
# Friedman test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ transformation_method, value.var="value_rank",
  fun.aggregate = mean
)

h_transformation <- friedman.test(as.matrix(data[, "dataset" := NULL]))
```

Considering single process parameters, the choice of learner (Wilcoxon signed rank test: $p < 10^{-8})$) and normalisation method (Wilcoxon signed rank test: $p = 0.03$) had a significant impact (at significance level $p = 0.05$), but transformation method (Friedman test: $p=0.11$) did not.

@@

```{r include = FALSE, eval = FALSE}
# CANDIDATE FOR REMOVAL !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

# Convert to data matrix. First aggregate within each experiment because the
# Wilcoxon signed rank test is not for repeated measurements.
data <- data.table::dcast(
  data,
  dataset ~ learner + transformation_method + normalisation_method, value.var="value_rank",
  fun.aggregate = mean
)
data[, "dataset" := NULL]

# Compute p-values through pair-wise comparison.
config_pairs <- utils::combn(colnames(data), m = 2L)
test_data <- apply(
  config_pairs,
  MARGIN = 2,
  function(config_pair, data) {
    h <- stats::wilcox.test(
      x = data[[config_pair[1L]]],
      y = data[[config_pair[2L]]],
      paired = TRUE,
      alternative = "two.sided"
    )

    return(data.table::data.table(
      "config_1" = config_pair[1L],
      "config_2" = config_pair[2L],
      "raw_p_value" = h$p.value
    ))
  },
  data = data
)
test_data <- data.table::rbindlist(test_data)

# Perform multiple testing correction.
test_data[, "p_value_corrected" := stats::p.adjust(raw_p_value)]
```
